### 2022-09-20 main/chapter_context.tex
write some about higgs

>>>>

The Higgs boson couples to an extraordinary variety of fundamental particles,
and \atlas' designers achieved discovery sensitivity across the entire
$m_H \in 100\textrm{--}1000\,\eV[G]$
window by targetting decays including
$H\to b\bar b$,
$H\to \gamma\gamma$,
$H\to ZZ^* \to 4\ell$, and
$H\to ZZ \to \ell\ell\nu\nu$.
This spectrum demands precise measurements of leptons, photons, and
$b$-jets, as well as sensitivity to the missing transverse momentum of
invisible neutrinos for $ZZ \to \ell\ell\nu\nu$ decays at the very highest
masses.

% Famously, \atlas\ and \cms\ have since found a Higgs boson candidate at
% $m_H = 125\,\eV[G]$~\cite{
% }
% with all of its predicted Standard Model properties~\cite{
% }.
